Designing Modular Software: A Case Study in Introductory Statistics

### 2016-12-09 jcgs-paper-2016/final_submission/paper.tex
Final final submission

Modern web technologies have enabled a new generation of software
packages that reside solely on the web, which eliminates the issue of
local installation and helps abstract away some of the more challenging
programming aspects of working directly with R. Upon the release of
RStudio's Shiny (RStudio, Inc. 2014) it became easier for an R-based
analysis to be converted to an interactive web application. Several
recent software packages have built upon Shiny to provide a web-based
system based on R. One such package is iNZight Lite (Wild 2015) which
attempts to expose students to data analysis without requiring
programming knowledge. inZight Lite is currently partially but not fully
reproducible. Another package is called Radiant (Nijs 2016), which is a
very promising web-based application with the aim of furthering business
education and financial analysis. While the application is modular and
extensible, it does require local installation and hosting. Radiant is a
business analytics platform with a host of functionality, while
\textbf{intRo} focuses on being a simple and extensible web tool for
learning. An overview of the comparison between the features of these
statistical software packages is presented in Table \ref{tab:compare}.
Partial fulfillment of requirements is noted in the table, as well as a
measure of the complexity of functionality offered by default. For
example, \texttt{R} does have an associated Graphical User Interface
(GUI), however this interface is very limited, thus only partially
fulfilling the behavior of a GUI.

>>>>

Modern web technologies have enabled a new generation of software
packages that reside solely on the web, which eliminates the issue of
local installation and helps abstract away some of the more challenging
programming aspects of working directly with R. Upon the release of
RStudio's Shiny (RStudio, Inc. 2014) it became easier for an R-based
analysis to be converted to an interactive web application. Several
recent software packages have built upon Shiny to provide a web-based
system based on R. One such package is iNZight Lite (Wild 2015) which
attempts to expose students to data analysis without requiring
programming knowledge. inZight Lite is currently partially but not fully
reproducible. Another package is called Radiant (Nijs 2016), which is a
very promising web-based application with the aim of furthering business
education and financial analysis. While the application is modular and
extensible, it does require local installation and hosting. Radiant is a
business analytics platform with a host of functionality, while
\texttt{intRo} focuses on being a simple and extensible web tool for
learning. An overview of the comparison between the features of these
statistical software packages is presented in Table \ref{tab:compare}.
Partial fulfillment of requirements is noted in the table, as well as a
measure of the complexity of functionality offered by default. For
example, R does have an associated Graphical User Interface (GUI),
however this interface is very limited, thus only partially fulfilling
the behavior of a GUI.

### 2016-12-09 jcgs-paper-2016/paper.Rmd
Final final submission

Modern web technologies have enabled a new generation of software packages that reside solely on the web, which eliminates the issue of local installation and helps abstract away some of the more challenging programming aspects of working directly with R. Upon the release of RStudio's Shiny [@shiny] it became easier for an R-based analysis to be converted to an interactive web application. Several recent software packages have built upon Shiny to provide a web-based system based on R. One such package is iNZight Lite [@inzight] which attempts to expose students to data analysis without requiring programming knowledge. inZight Lite is currently partially but not fully reproducible. Another package is called Radiant [@radiant], which is a very promising web-based application with the aim of furthering business education and financial analysis. While the application is modular and extensible, it does require local installation and hosting. Radiant is a business analytics platform with a host of functionality, while **intRo** focuses on being a simple and extensible web tool for learning. An overview of the comparison between the features of these statistical software packages is presented in Table \ref{tab:compare}. Partial fulfillment of requirements is noted in the table, as well as a measure of the complexity of functionality offered by default. For example, `R` does have an associated Graphical User Interface (GUI), however this interface is very limited, thus only partially fulfilling the behavior of a GUI.

>>>>

Modern web technologies have enabled a new generation of software packages that reside solely on the web, which eliminates the issue of local installation and helps abstract away some of the more challenging programming aspects of working directly with R. Upon the release of RStudio's Shiny [@shiny] it became easier for an R-based analysis to be converted to an interactive web application. Several recent software packages have built upon Shiny to provide a web-based system based on R. One such package is iNZight Lite [@inzight] which attempts to expose students to data analysis without requiring programming knowledge. inZight Lite is currently partially but not fully reproducible. Another package is called Radiant [@radiant], which is a very promising web-based application with the aim of furthering business education and financial analysis. While the application is modular and extensible, it does require local installation and hosting. Radiant is a business analytics platform with a host of functionality, while `intRo` focuses on being a simple and extensible web tool for learning. An overview of the comparison between the features of these statistical software packages is presented in Table \ref{tab:compare}. Partial fulfillment of requirements is noted in the table, as well as a measure of the complexity of functionality offered by default. For example, R does have an associated Graphical User Interface (GUI), however this interface is very limited, thus only partially fulfilling the behavior of a GUI.
